% Content Template Version: 3.7.0
\begin{letter}{\recipientaddress}

\thispagestyle{fancy}  % Override letter.cls firstpage style to show header

% Adjust vertical position for fixed alignment (e.g., window envelope; test value)
  \vspace*{-0.5cm}  % Shift down ~5cm from top for recipient to hit window (~9.5cm total from page top)
  
  % No global \vspace* here—handled in \opening for absolute

	\opening{\salutation}  % Or direct body here

	\subjectline  % Insert subject below salutation
 
I am \textbf{\sendername}, Chief Executive Officer and Chief Technology Officer of \textbf{Example Tech Company} (legally
registered as \textbf{Example Business Solutions LLC}, established on 1 January 2021, under Registration No. 123456 and National ID 9876543210, operating in the United Kingdom). We are dedicated to harnessing innovative technology to empower
communities and drive positive change. It is with great enthusiasm that I reach out to the Department of Social Services,
recognising your pivotal role in supporting vulnerable individuals and fostering societal well-being. Our shared commitment
to making a tangible difference inspires this proposal, as we envision a partnership that could transform service delivery
through cutting-edge digital solutions.

Imagine streamlining access to essential resources, enhancing data-driven decision-making, and ultimately amplifying the
impact of your vital work. At Example Tech Company, we have developed tailored platforms that have already assisted similar
organisations in reducing administrative burdens by up to 40\% and improving outreach efficiency. We would be honoured to
collaborate with your team to customise these tools for your needs, creating a brighter future for those you serve. I am
eager to discuss this opportunity further and explore how we can work together to achieve extraordinary outcomes.

\closing{\closingphrase}
 

\end{letter}
